---
title: "LDA (DTM >5) "
subtitle: " "
author: Min Tang
date: last-modified
format: pdf
execute: 
  
  message: false
  warning: false
  echo: false
editor: 
  markdown: 
    wrap: sentence
---

#Loading

```{r}
#| echo: false
#| message: false
#| warning: false
# Load libraries
library(flextable)
library(officer)
library(modelsummary)
library(dplyr)
library(knitr)
library(kableExtra)
library(tibble)
library(tidyverse)
library(quanteda)
library(topicmodels)
library(jsonlite)
library(stringr)
library(ggplot2)
library(purrr) #for?
library(tidyr)
library(data.table)
library(glue)
library(tidygraph)
library(ggraph)
library(slam)         # New: needed for perplexity calc
library(topicdoc) 
library(Matrix)
library(tm)
library(mlbench)
library(elasticnet) 
library(mclust) 
library(cluster)

```

```{r}
# file path
# =================
data_dir <- '/Users/a1-6/Desktop/CSS/1.Thesis/Data/'
#setwd(data_dir)
business <- paste0(data_dir,'merged_ph_dataclean0319.csv') #list()
user <- paste0(data_dir,'user_stat0319.csv')
review <- paste0(data_dir,'all_philly_reviews.csv')

```

## 1.PH Stats
This is a list of users' visiting history, including business attributes, and users' attributes, review text and friends.Please note that user or business can be duplicated.

```{r}
#all records of users and their business visited(user id or business id can be duplicated)
business_dt<-read.csv(business)
dim(business_dt) #280112

```

###1.1 Business-Level Data(unique business?)

```{r}
# PH Business-Level Data (Unique ID)
# ==================================

uni_business <- business_dt |> distinct(business_id, .keep_all = TRUE) |> select(-user_id)
head(uni_business)
nrow(uni_business) #4387



num_vars_business <- uni_business |> 
  select(stars_restaurant, review.count_restaurant, price_level,cat_count_restaurant)
#sum(is.na(num_vars_business))

desc_table1 <- data.frame(
  Statistic = c("N", "Mean", "SD", "Median", "Min", "Max"),
  restaurant_category_count = c(
    nrow(num_vars_business),
    #sum(unique(num_vars_business$bs_cat_count)),
    mean(num_vars_business$cat_count_restaurant, na.rm = TRUE),
    sd(num_vars_business$cat_count_restaurant, na.rm = TRUE),
    median(num_vars_business$cat_count_restaurant, na.rm = TRUE),
    min(num_vars_business$cat_count_restaurant, na.rm = TRUE),
    max(num_vars_business$cat_count_restaurant, na.rm = TRUE)
  ),
   restaurant_star = c(
    nrow(num_vars_business),
    mean(num_vars_business$stars_restaurant, na.rm = TRUE),
    sd(num_vars_business$stars_restaurant, na.rm = TRUE),
    median(num_vars_business$stars_restaurant, na.rm = TRUE),
    min(num_vars_business$stars_restaurant, na.rm = TRUE),
    max(num_vars_business$stars_restaurant, na.rm = TRUE)
  ),
  restaurant_review_count = c(
    #length(num_vars_business$review_count),
    nrow(num_vars_business),
    mean(num_vars_business$review.count_restaurant, na.rm = TRUE),
    sd(num_vars_business$review.count_restaurant, na.rm = TRUE),
    median(num_vars_business$review.count_restaurant, na.rm = TRUE),
    min(num_vars_business$review.count_restaurant, na.rm = TRUE),
    max(num_vars_business$review.count_restaurant, na.rm = TRUE)
  ),
  
  price_level = c(
    nrow(num_vars_business),
    mean(num_vars_business$price_level, na.rm = TRUE),
    sd(num_vars_business$price_level, na.rm = TRUE),
    median(num_vars_business$price_level, na.rm = TRUE),
    min(num_vars_business$price_level, na.rm = TRUE),
    max(num_vars_business$price_level, na.rm = TRUE)
  )
) 
#desc_table1
```

### 1.2 User-Level Data

```{r}
# PH User-Level Data (Unique ID)
# ==================================
user_dt<- read.csv(user)

dim(user_dt)#25034
#colnames(user_dt)
head(user_dt,2)


num_vars_user <-user_dt |> select(review_count_median,restaurant_star_median,restaurant_cat_median,price_level_median,user_star_median,user_cat_count,user_visit_count,friend_count)

desc_table2 <- data.frame(
  Statistic = c("N", "Mean", "SD", "Median", "Min", "Max"),
  user_review_count = c(
    nrow(num_vars_user),
    mean(num_vars_user$review_count_median, na.rm = TRUE),
    sd(num_vars_user$review_count_median, na.rm = TRUE),
    median(num_vars_user$review_count_median, na.rm = TRUE),
    min(num_vars_user$review_count_median, na.rm = TRUE),
    max(num_vars_user$review_count_median, na.rm = TRUE)
  ),
  restaurant_visit_star = c( #restaurant's rating star that users visited 
    nrow(num_vars_user),
    mean(num_vars_user$restaurant_star_median, na.rm = TRUE),
    sd(num_vars_user$restaurant_star_median, na.rm = TRUE),
    median(num_vars_user$restaurant_star_median, na.rm = TRUE),
    min(num_vars_user$restaurant_star_median, na.rm = TRUE),
    max(num_vars_user$restaurant_star_median, na.rm = TRUE)
  ),
  price_level = c(
    nrow(num_vars_user),
    mean(num_vars_user$price_level_median, na.rm = TRUE),
    sd(num_vars_user$price_level_median, na.rm = TRUE),
    median(num_vars_user$price_level_median, na.rm = TRUE),
    min(num_vars_user$price_level_median, na.rm = TRUE),
    max(num_vars_user$price_level_median, na.rm = TRUE)
  ),
 user_category_count = c(  #restaurant category number that users visited 
    nrow(num_vars_user),
    #sum(num_vars_user$user_cat_count),
    mean(num_vars_user$user_cat_count, na.rm = TRUE),
    sd(num_vars_user$user_cat_count, na.rm = TRUE),
    median(num_vars_user$user_cat_count, na.rm = TRUE),
    min(num_vars_user$user_cat_count, na.rm = TRUE),
    max(num_vars_user$user_cat_count, na.rm = TRUE)
  ),
 restaurant_visit_count = c(  #restaurant number that users visited 
    nrow(num_vars_user),
    mean(num_vars_user$user_visit_count, na.rm = TRUE),
    sd(num_vars_user$user_visit_count, na.rm = TRUE),
    median(num_vars_user$user_visit_count, na.rm = TRUE),
    min(num_vars_user$user_visit_count, na.rm = TRUE),
    max(num_vars_user$user_visit_count, na.rm = TRUE)
  ),
  friend_count = c(
    nrow(num_vars_user),
    #sum(num_vars_user$friend_count),
    mean(num_vars_user$friend_count, na.rm = TRUE),
    sd(num_vars_user$friend_count, na.rm = TRUE),
    median(num_vars_user$friend_count, na.rm = TRUE),
    min(num_vars_user$friend_count, na.rm = TRUE),
    max(num_vars_user$friend_count, na.rm = TRUE)
  )
)
#desc_table2
```

### 1.3. User Review Data

```{r}
# PH User  Review
# ==================================
review_dt<- read.csv(review)
head(review_dt)

user_review <- review_dt  |> 
  semi_join(business_dt, by = "user_id")  |> 
  filter(nchar(as.character(text)) > 0) |> 
  select(-date)
#head(user_review)#485191
user_review$review_length <- nchar(as.character(user_review$text))


desc_table3 <- data.frame(
  Statistic = c("N", "Mean", "SD", "Median", "Min", "Max"),
  review_length = c(
    nrow(user_review),
    mean(user_review$review_length, na.rm = TRUE),
    sd(user_review$review_length, na.rm = TRUE),
    median(user_review$review_length, na.rm = TRUE),
    min(user_review$review_length, na.rm = TRUE),
    max(user_review$review_length, na.rm = TRUE)
    )) 

```


### 1.4 DS
```{r}
process_table <- function(df, group_name) {
  df  |> 
    pivot_longer(-Statistic, names_to = "Variable", values_to = "Value") |> 
     pivot_wider(names_from = Statistic, values_from = Value) |> 
    mutate(
      Group = group_name,
      Variable = case_when(
        Variable == "restaurant_star" ~ "Restaurant Star",
        Variable == "restaurant_review_count" ~ "Restaurant Review Number",
        Variable == "price_level" ~ "Price ($-$$$$)",
        Variable == "restaurant_visit_star" ~ "Restaurant_Visited Star",
        Variable == "restaurant_category_count" ~ "Restaurant Category Number",
        Variable == "user_review_count" ~ "User Review Number",
        Variable == "user_category_count" ~ "User Category Number",
        Variable == "restaurant_visit_count" ~ "Restaurant_Visited Number",
        Variable == "friend_count" ~ "Friend Number",
        Variable == "review_length" ~ "User Review Text Length",
        TRUE ~ Variable
      )
    ) |> 
    select(Group, Variable, N, Mean, SD, Median,Min, Max)
}


desc_table1 <- process_table(desc_table1, "Restaurants")
desc_table2 <- process_table(desc_table2, "Users")
desc_table3 <- process_table(desc_table3, "Reviews")

final_table <- bind_rows(desc_table1, desc_table2, desc_table3) |>
  mutate(across(c(Mean, SD,Median, Min, Max), ~ round(as.numeric(.), 1)))


tbl1<- final_table  |> 
  flextable() |> 
  merge_v(j = "Group") |> 
  font(fontname = "Times New Roman", part = "all")|> 
  fontsize(size = 10, part = "all") |> 
  bold(part = "header")|> 
  width(j = 2, width = 1.2) |>   #column 1st
  autofit() |> 
  set_caption("Decriptive Statistics of Business, User & Review Distribution") |> 
  add_footer_lines("Note: Data From Yelp in Philadelphia.")
```



# 2. LDA - Latent Dirichlet Allocation


### 2.1 User-Business Matrix for LDA (DTM > 5)

- Transform matrix into DTM format;
- Choose users who have more than 5 visits and businesses that have more than 5 reviews

```{r}


user_business_matrix <- readMM(paste0(data_dir,'User_Business_Matrix0319.mtx'))

row_users <- read.csv(paste0(data_dir,'row_user.csv'), header = FALSE)[,1]#all rows on 1st column
col_business <- read.csv(paste0(data_dir,'col_business.csv'), header = FALSE)[,1]#all rows on 1st column
rownames(user_business_matrix) <- row_users
colnames(user_business_matrix) <- col_business
#dim(user_business_matrix) #25034  4387


dtm <- as.DocumentTermMatrix(user_business_matrix,weighting = weightTf)
#class(dtm) #"DocumentTermMatrix"    "simple_triplet_matrix"

#delete business under certain visits and same as user 
dtm <- dtm[, slam::col_sums(dtm) > 5]
dtm <- dtm[slam::row_sums(dtm)  > 5, ] 
dim(dtm) #  14370  3549[5]

#filtered_businesses <- colnames(dtm)
#write.csv(filtered_businesses,
  #        "filtered_business_list(after dtm).csv",
   #       row.names = FALSE)

```

### 2.2 K Selection
- Perplexity: if a "elbow" point shows in plot of perplexity, topics are good fit 
- Topic coherance: if higher, easier intepretation
- JSD: if higher JSD, topics are distinguished better
```{r}
library(textmineR) 

# Perplexity & Probabilistic Coherence
# ==============================================
#80/20 Train & Test data for ptrplexity
set.seed(123)
n <- nrow(dtm)
idx <- sample(seq_len(n), size = floor(0.8 * n))
tr_dt <- dtm[idx, , drop = FALSE]
tst_dt  <- dtm[-idx, , drop = FALSE] 

ks <- c(2,10,20,35,50,65,100)

perp <- c()
mean_coherence <- c()
for(i in 1:length(ks)){
  # Train
  current_tm <- LDA(x = tr_dt,
                    k = ks[i],
                    method="Gibbs",
                    control=list(iter = 500,
                                 seed = 123,verbose = 200))
  
  perp[i] <- perplexity(object = current_tm,
                        newdata = as.simple_triplet_matrix(tst_dt)) # perplexity() wants the test data in simple_triplet_matrix format.
  
  coh <- topic_coherence(current_tm, tr_dt, top_n_tokens = 10)
  mean_coherence[i] <- mean(coh, na.rm = TRUE)
 # print(perp)
#  print(round(mean_coherence[i], 3))
}


#Jensen-Shannon Divergence to calculate between-topics similairty
# ==============================================
calculate_topic_jsd <- function(lda_model) {
  topic_word_dist <- topicmodels::posterior(lda_model)$terms
  n_topics <- nrow(topic_word_dist)
  jsd_values <- c()
  
  for(i in 1:(n_topics-1)) {
    for(j in (i+1):n_topics) {
      p <- topic_word_dist[i, ]
      q <- topic_word_dist[j, ]
      
      p <- p / sum(p)
      q <- q / sum(q)
      
      m <- 0.5 * (p + q)
      jsd <- 0.5 * sum(p * log(p / m)) + 0.5 * sum(q * log(q / m))
      jsd_values <- c(jsd_values, jsd)
    }
  }
  return(mean(jsd_values))
}

ks <- c(2,10,20,35,50,65,100)
jsd_results <- data.frame(K = ks, mean_jsd = NA)

mean_jsd<-c()
for(i in 1:length(ks)) {
  lda_temp <- LDA(x = tr_dt, 
                  k = ks[i], 
                  method = "Gibbs",
                  control = list(iter = 500, seed = 123))
  mean_jsd[i] <- calculate_topic_jsd(lda_temp) 
}
```


```{r}
#plot
k_plot <- data.frame(
  K = ks,
  Perplexity = perp,
  Coherence = mean_coherence,
  JSD = mean_jsd)

k_plot_long <- k_plot |>
  pivot_longer(cols = c(Perplexity, Coherence, JSD),
               names_to = "Metric",
               values_to = "Value")

fig1 <- ggplot(k_plot_long, aes(x = K, y = Value)) +
  geom_line(color = "blue") +
  geom_point() +
  facet_wrap(~ Metric, scales = "free_y", ncol = 3) + #independent y-axis
  labs(
    #title = "K Selection Comparison for LDA Topic Number",
    x = "Number of Topics (K)",
    y = "Value") +
  theme(
    #plot.title = element_text(size = 15, face = "bold", hjust = 0.5),
    strip.text = element_text(size = 15, face = "bold"))

```



```{r}
#  LDA=50
#=============================
set.seed(123) 
K <- 50
lda <- LDA(x = dtm, 
             k = K, 
             method="Gibbs",
             control=list(iter = 1000, 
                          seed = 123, 
                          verbose = 500),
                          alpha = 0.1) #short/sparse text
                          
lda_posterior <- topicmodels::posterior(object = lda)

#topic-word distribution, word =（P(restaurant | taste topic)）;
topic_distr_over_words <- lda_posterior$terms

topic_distr_over_words_dt <- data.table(topic = 1:nrow(topic_distr_over_words), topic_distr_over_words)
topic_distr_over_words_dt <- melt.data.table(
  topic_distr_over_words_dt,
  id.vars = "topic",
  variable.name = "Word",          
  value.name = "Probability"      )

# user_topic_dist =（P( topic | user doc)
topic_distr_over_doc <- lda_posterior$topics#matrix:
#summary(topic_distr_over_doc)

user_topic_df <- topic_distr_over_doc |> 
  as.data.frame() |> 
  rownames_to_column("user_id") # Probability of 50 Topics

```

## 2.3 User Topic Distribution (taste topics)

```{r}
#Business x Attribute
#========================
bs_attr<-read.csv(paste0(data_dir,'Business_attribute0319.csv'))
head(bs_attr)
#pivot table & create price_taste
bs_attr_long <- bs_attr |> 
  pivot_longer(cols = -c(business_id, price_level), 
               names_to = "taste", 
               values_to = "value") |> 
  filter(value>0) |>
  group_by(business_id) |>
  mutate(price_taste = paste0("P", price_level,"_",taste)) |> 
  select(business_id,price_taste,price_level,taste)

#cat("There are", length(unique(bs_attr_long$price_taste)),"unique combination s of taste and price.\n")#240 

#each topic (taste) contains the word(restaurant) probability
top8_interest_topic <- topic_distr_over_words_dt |> 
  group_by(topic) |> 
   slice_max(order_by = Probability, n = 8)  

top8_business_attr <- top8_interest_topic |> 
  rename(business_id = Word) |> 
  left_join(bs_attr_long, by = "business_id", relationship = "many-to-many") |>
  group_by(topic,business_id) |>  
  summarise(
    price_taste = paste(unique(price_taste), collapse = ", "),
    Probability = first(Probability),
    taste =paste(unique(taste), collapse = ", "),
    price_level=paste(unique(price_level), collapse = ", "),
    .groups = "drop"
  ) |>
  arrange(topic, desc(Probability)) |> 
  mutate(probability = Probability) |> 
  select(topic,price_taste,taste,price_level,probability)


```

## 2.4 Topic Qualitative Analysis
```{r}
library(stringr)
library(reshape2)

civ_type <- function(taste_string) {
  civ <- list(
    `American` = str_count(taste_string, regex("American|Cheesesteaks|Southern", ignore_case = TRUE)),
    `European` = str_count(taste_string, regex("French|German|Belgian|Irish|British|Modern\\.European|Greek|Spanish|Italian|Pizza|Tapas|Creperies", ignore_case = TRUE)),
    `Latin American` = str_count(taste_string, regex("Mexican|Latin\\.American|Caribbean|Cuban|Brazilian|Peruvian|Tex\\.Mex|Tacos", ignore_case = TRUE)),
    `Asia`= str_count(taste_string, regex("Chinese|Cantonese|Dim\\.Sum|Szechuan|Shanghainese|Hong\\.Kong|Taiwanese|Japanese|Sushi\\.Bars|Ramen|Pan\\.Asian|Hot\\.Pot|Thai|Vietnamese|Korean|Malaysian|Singaporean|Asian\\.Fusion", ignore_case = TRUE)),
    `Middle Eastern` = str_count(taste_string, regex("Middle\\.Eastern|Lebanese|Israeli|Halal|Kebab", ignore_case = TRUE)),
    `Other Ethnic`   = str_count(taste_string, regex("African|Indian|Pakistani|Ethnic\\.Food|Mongolian", ignore_case = TRUE)),
    `Other` = str_count(taste_string, regex("Specialty\\.Food|Noodles|Buffets|Seafood|Sandwiches|Soul\\.Food|Comfort\\.Food|Burgers", ignore_case = TRUE))
  )
  civ_df <- tibble(
    civilization = names(civ),
    score = as.numeric(civ)
  ) |> 
    filter(score > 0) |> 
    arrange(desc(score))
  
  if (nrow(civ_df) == 0) {
   # warning(paste("No match", taste_string)) 
    return("Other")
  }
  
  max_score <- max(civ_df$score)
  top_civs <- civ_df |> filter(score == max_score) |> pull(civilization)
  if (length(top_civs) >= 2) {
    return(paste(top_civs, collapse = " + "))
  }
  
  top_civ <- top_civs[1]
  
  if (nrow(civ_df) >= 2 && civ_df$score[2] >= 2) {
    second <- civ_df$civilization[2]
    return(paste(top_civ, "+", second))
  }
  
  return(top_civ)
}
  

top8_with_civ <- top8_business_attr |>
  mutate(civ_group = map_chr(taste, civ_type))|>
  group_by(topic) |>
  summarise(
    main_civ = civ_group[which.max(probability)],
    main_taste = taste[which.max(probability)],
    main_price = price_level[which.max(probability)],
    main_prob = max(probability),
    
    all_tastes = paste(unique(civ_group), collapse = " | "),
    .groups = "drop"
  ) |>
  arrange(topic)


```


```{r}

topic_civ <- top8_with_civ |>
  group_by(main_civ) |>
  summarise(
    topics = paste(topic, collapse = ", "),
    words = paste0(main_taste," (P", main_price,")", collapse = "; "),
    n_topics = n(),
    .groups = "drop"
  ) |> 
    select(main_civ, topics,words)
print(topic_civ)


ggplot(data = topic_civ, aes(x = main_civ, y = n_topics)) + 
  geom_bar(stat = "identity")


user_civ <- user_topic_df %>% 
  mutate(user_id = rownames(.)) %>% 
  pivot_longer(cols = -user_id, names_to = "topic", values_to = "prob") %>%
  mutate(topic = as.numeric(str_remove(topic, "V"))) %>%
  left_join(topic_to_civ, by = "topic") %>%
  group_by(user_id, main_civ) %>%
  summarise(prob = sum(prob), .groups = "drop") %>%
  pivot_wider(id_cols = user_id, names_from = main_civ, values_from = prob, values_fill = 0)  
  
```


```{r}
topics <- c(1, 7)
tbl6 <-top8_business_attr |> filter(topic %in% topics)|>
  select(topic,taste,price_level,probability) |> 
flextable() |>
  font(fontname = "Times New Roman", part = "all")|> 
  fontsize(size = 10, part = "all") |> 
  bold(part = "header")|> 
  width(j = 1, width = 1.5) |>  
  autofit() |> 
  set_caption("Topic & Word Example") |> 
  add_footer_lines("Note: Data From Yelp in Philadelphia.")

 
tbl7 <-topic_civ|>
flextable() |>
  font(fontname = "Times New Roman", part = "all")|> 
  fontsize(size = 10, part = "all") |> 
  bold(part = "header")|> 
   width(j = 3, width = 1.5) |>  
  autofit() |> 
  set_caption("Topic Name Example") |> 
  add_footer_lines("Note: Data From Yelp in Philadelphia.")


tbl8 <-top8_with_civ[1:5,] |> 
  flextable() |>
  font(fontname = "Times New Roman", part = "all")|> 
  fontsize(size = 10, part = "all") |> 
  bold(part = "header")|> 
  width(j = 1, width = 1.5) |>  
  autofit() |> 
  set_caption("Topic Summary Example") |> 
  add_footer_lines("Note: Data From Yelp in Philadelphia.")


```



```{r}
library(ineq)
gini_values <- user_civ |>
   mutate(gini = apply(user_topic_df[, -1], 1, function(x) Gini(x)))  #apply(user_topic_df[, -1], 1, function(x) Gini(x))) ???

# Gini Distribution of Users
# ==============================================
fig7 <-ggplot(data = gini_values, aes(x = gini)) +
  geom_histogram(bins = 10, color = "black", fill = "darkgrey") +
  stat_bin(aes(label = after_stat(count)), 
           geom = "text", 
           bins = 10,
           vjust = -0.5,  
           size = 3) +
  geom_vline(xintercept = 0.3, 
             color = "red", 
             linetype = "dashed", 
             linewidth = 1) +
   labs(x = "Gini Coefficient", y = "Count")+
      # title = "Distribution of User Topic Gini Coefficients") +
  theme_minimal()+
  theme(strip.text = element_text(size = 12, face = "bold"))


```


```{r}
set.seed(123)
#Gini = 0.3
user_03 <- gini_values |> 
  filter(gini == 0.3) |> 
  sample_n(1) |>
  pivot_longer(cols = - c(user_id,gini), names_to = "topic", values_to = "prob") 

fig4<-ggplot(user_03, aes(x = topic, y = prob)) +
  geom_bar(stat = "identity") +
  ylim(0, 0.5) +
  facet_wrap(~ paste0("Gini Coefficient = ", round(gini, 3))) +
  labs(x = "Topics", 
      y = "Probability")+
  theme(strip.text = element_text(size = 25, face = "bold"),
          axis.title = element_text(size = 12), 
        axis.text.x  = element_text(angle = 45,hjust = 1,size = 12))

#Bottom 30% Gini
user_omni <- gini_values |> 
  filter(gini < quantile(gini_values$gini, 0.3)) |> 
  sample_n(1) |>
  pivot_longer(cols = - c(user_id,gini), names_to = "topic", values_to = "prob") 

fig5<-ggplot(user_omni, aes(x = topic, y = prob)) +
  geom_bar(stat = "identity") +
  ylim(0, 0.5) +
  facet_wrap(~ paste0("Gini Coefficient = ", round(gini, 3))) +
  labs(x = "Topics", 
      y = "Probability")+
  theme(strip.text = element_text(size = 25, face = "bold"),
          axis.title = element_text(size = 12), 
         axis.text.x  = element_text(angle = 45,hjust = 1,size = 12))

#Gini > 0.4
user_high <- gini_values |> 
  filter(gini > 0.4) |> 
  sample_n(1) |>
  pivot_longer(cols = - c(user_id,gini), names_to = "topic", values_to = "prob") 

fig6<-ggplot(user_other, aes(x = topic, y = prob)) +
  geom_bar(stat = "identity") +
  ylim(0, 0.5) +
  facet_wrap(~ paste0("Gini Coefficient = ", round(gini, 3))) +
  labs(x = "Topics", 
      y = "Probability")+
  theme( strip.text = element_text(size = 25, face = "bold"))

```


## 2.5 Omnivores by "Gini"
We use 50 topics and bottom 30th pencitile of Gini coefficient, and to catogorize the user 50 topics. According to omnivores definition, their consumptions cross the taste types and price levels.

```{r}
#filter the users >= 2 price level
user_price_diversity <- business_dt |> 
  group_by(user_id) |> 
  summarise(
    n_price_levels = n_distinct(price_level, na.rm = TRUE),
    .groups = "drop"
  ) |> 
  filter(n_price_levels >= 2) 

user_topic_df <- user_topic_df |> 
  filter(user_id %in% user_price_diversity$user_id)

#cat("Users with price with >= 2 price levels:", nrow(user_topic_df))


# Residualized Gini
# ==============================================
 user_gini<- user_topic_df |>
   mutate(gini = apply(user_topic_df[, -1], 1, function(x) Gini(x))) 

#aggregate user information into one dataframe
user_gini_df <- user_gini |>  left_join(user_dt,by = "user_id")


model_gini <- lm(gini ~ log(user_visit_count + 1) , data = user_gini_df )
#summary(model_gini)
user_gini_df$predicted_gini <- predict(model_gini, newdata = user_gini_df)
user_gini_df$gini2 <- user_gini_df$gini - user_gini_df$predicted_gini

```


```{r}
#| label: tbl-gini

gini_table <-user_gini_df |> 
          summarise(
            Variable = c("Orginal Gini","Residualized Gini"),
            N = c(n(), n()),
            Median = c(median(gini),median(gini2)),
            Mean = c(mean(gini),mean(gini2)),
            IQR    = c(IQR(gini),IQR(gini2)),
            Min = c(min(gini),min(gini2)),
            Max = c(max(gini),max(gini2))) |> 
  mutate(across(Median:Max, ~ round(., 3)))


tbl2 <- gini_table  |> 
  flextable()  |> 
  font(fontname = "Times New Roman", part = "all")|> 
  fontsize(size = 10, part = "all") |> 
  bold(part = "header")|> 
  width(j = 1, width = 1.5) |>   #column 1st
  autofit() |> 
  set_caption("Gini Coefficient Statistics") |> 
  add_footer_lines("Note: Data From Yelp in Philadelphia.")

print(tbl2)


#Gini Distribution
# ==============================================
# ggplot(data = user_gini_df, aes(x = gini2)) +
#   geom_histogram(bins = 15, color = "black", fill = "darkgrey") +
#   stat_bin(aes(label = after_stat(count)), 
#            geom = "text", 
#            bins = 15,
#            vjust = -0.5,  
#            size = 3) +
#   geom_vline(xintercept = omnivore_threshold, 
#              color = "red", 
#              linetype = "dashed", 
#              linewidth = 1) +
#    labs(x = "Gini Coefficient", y = "Count")+
#       # title = "Distribution of User Topic Gini Coefficients") +
#   theme_minimal()+
#   theme(strip.text = element_text(size = 15, face = "bold"))
```


```{r}
# Omnivore groups within lowest 30% Residualized Gini
omnivore_threshold <- quantile(user_gini_df$gini2, 0.3)
omnivore_user <- user_gini_df |>
  filter(gini2 < omnivore_threshold) |>
  select(user_id)

cat("There are", nrow(omnivore_user), "omnivore users.", round(nrow(omnivore_user) / nrow(user_gini_df) * 100,2), "% of all users are omnivores(Gini index threshold:",round(omnivore_threshold,3),").\n")

```





# Export 

```{r}
#output as rds 
#===================
output_path <-paste0(data_dir, 'Code for replication')
output_path_m<-paste0(data_dir, 'Code for replication/model')


#K for LDA
k_selection_results <- list(
  ks = ks,
  perplexity = perp,
  coherence = mean_coherence,
  jsd = mean_jsd
)
saveRDS(k_selection_results, file = paste0(output_path_m, 'K selection for LDA_100.rds'))


#LDA Model(5) 
#============
#lda model
saveRDS(lda, file = paste0(output_path_m, '/lda_model_k50.rds'))
saveRDS(user_topic_df,file = paste0(output_path_m, '/user_topic_df.rds'))

#lda model_all
saveRDS(object = list(user_business_matrix=user_business_matrix,
                      dtm=dtm, 
                      lda=lda,
                      k=k,
                      topic_distr_over_words_dt,
                      user_topic_df,
                      top8_business_attr= top8_business_attr), 
        file = paste0(output_path_m, '/lda_dtm_filter5.rds'))

## write.csv(top8_business_attr,
#           paste0(output_path,"/file/top8_business_topic50_dtm5.csv"), 
#                  row.names = FALSE)

#qualitative analysis with lda
saveRDS(object = list( 
                      user_civ,
                      topic_name_with_civ = top8_with_civ), 
        file = paste0(output_path_m, '/ldatopic_with_civ.rds'))



#Gini
saveRDS(omnivore_user, file = paste0(output_path_m,'/omnivore_user_list.rds'))
saveRDS(user_gini_df, file = paste0(output_path_m,'/user_gini_df.rds'))







```

```{r}
#output as png 
#===================
library(patchwork)

#no. 1
ggsave("LDA_K_Selection.png", fig1, dpi = 300,width = 15,height = 8)

#no. 2
k_plots <- fig2 + fig3 + 
  plot_annotation(tag_levels = "A")  
ggsave("Cluster_K_Selections400.png", k_plots, dpi = 300,width = 15,height = 8)

#no. 3
gini_plot <-  fig4+ fig5  +
  plot_layout(ncol = 2) +
  plot_annotation(
    caption = "Note: Data From Yelp in Philadelphia.",
    tag_levels = "A")
ggsave("User_Gini_Plots.png", dpi = 300,width = 20,height = 15)

#no. 4
ggsave("Gini Distribution of Users.png", fig7, dpi = 300,width = 15,height = 8)



#output as word doc
#===================
tbl_list <- list(tbl1, tbl2, tbl3, tbl4,tbl5, tbl6, tbl7, tbl8)

doc <- read_docx()
for (i in 1:length(tbl_list)) {
  doc <- doc |>
    body_add_par("") |>
    body_add_flextable(tbl_list[[i]])
}
doc <- doc |> body_add_par("")

print(doc, target = "Thesis_Tables2.docx")


```


